Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-01-13 tensor/draft/draft-tensor-op.tex
[tensor/draft] fix another file-name error, add comment

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH_1_6_vs_cT}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

Eventually we also explore the behaviour of derived constraints with respect
to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
this purpose we include also the branching ratio and the rate CP asymmetry
of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli
of vectorial couplings.

>>>>

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_cT}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

Eventually we also explore the behaviour of derived constraints with respect
to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli
of vectorial couplings.
